RSA_model2

### 2015-10-20 models/RSA_Model2.Rmd
update for running with e8 l0 listener and e6 prag listener :

library(knitr)
library(rjson)

opts_chunk$set(cache=TRUE)

source("analysis/useful_dplyr.R")
```

@@

  if (usenone) {
    mat$none <- c(0.8, 0.2, 0, 0, 0)
    #mat$bad <- c(.5, .9, .4, .1, 0)
  }

@@

Run model
---------
```{r}
md <- data %>%
  do(run.rsa(., alpha = 1, useprior = T, usenone = T))
```

Visualize
---------
```{r}
qplot(stars, listener.p, col=degree, 
      data=md, main="Model vs Human judgments\nSemantics measured empirically",
      ylab="Posteriors p( rating | word )") + 
  facet_wrap(~scale) + 
  geom_line(aes(y = pred), lty = 4)

>>>>

library(knitr)
library(rjson)
library(dplyr)
library(tidyr)

opts_chunk$set(cache=TRUE)
setwd("~/Desktop/Projects/scalar_implicature/")
source("analysis/useful_dplyr.R")
```

@@

  if (usenone) {
    mat$none <- c(1, 0, 0, 0, 0)
    #mat$meh <- c(0.0, 0.2, 0.6, 0.2, 0)
    #mat$bad <- c(.5, .9, .4, .1, 0)
  }

@@

Run model
---------
```{r}
alpha = 1
md <- data %>%
  do(run.rsa(., alpha = alpha, useprior = T, usenone = T))
```

Visualize
---------
```{r}
qplot(stars, listener.p, col=degree, 
      data=md,
      main=paste("Model vs Human judgments\nSemantics measured empirically\nalpha=",
                 alpha),
      ylab="Posteriors p( rating | word )") + 
  facet_wrap(~scale) + 
  geom_line(aes(y = pred), lty = 4)
